---
title: "PrioritizR"
format: html
editor: visual
---

Please contact sarahhalperin\@u.boisestate.edu if you have any questions. The code will need to be modified based on how you bring in the data.

## prioritizR

Systematic Conservation Prioritization in R: https://prioritizr.net/

Citation: Hanson JO, Schuster R, Morrell N, Strimas-Mackey M, Edwards BPM, Watts ME, Arcese P, Bennett J, Possingham HP (2022). prioritizr: Systematic Conservation Prioritization in R. R package version 7.2.2. Available at [https://CRAN.R-project.org/package=prioritizr](https://cran.r-project.org/package=prioritizr).

## Load Packages

```{r}
#install.packages("prioritizr", repos = "https://cran.rstudio.com/")
library(prioritizr)

#install.packages('/Library/gurobi952/macos_universal2/R/gurobi_9.5-2_R_4.2.0.tgz', repos=NULL)
library(gurobi)
library(ggplot2)
library(dplyr)
library(terra)
library(raster)
library(reshape)
library(sf)
library(patchwork)
library(ggnewscale)
library(knitr)
library(viridis)
library(wesanderson)



source("get_optim_function.R") #save in same folder as this script 


```

## Load Data

```{r}
Folder<-"/Volumes/JodiBrandt/Common/SarahHalperin/" #Base Folder 

#---------------------------------------#
#Study Area
StudyArea<-st_read(paste0(Folder, "Data/StudyArea/StudyArea_wgs84.shp"))
StudyArea.sf<-st_transform(StudyArea, "epsg:5070")
#---------------------------------------#
new.ras<-terra::rast(xmin=-1674495, xmax=-1594155, ymin=2404755,ymax=2505645, resolution=1000, crs=crs(StudyArea.sf)) #Base raster for resampling and projecting 


#---------------------------------------#
#Productivity, Versatility, Resilience
PVR_TV<-terra::rast(paste0(Folder, "/Data/AFT_Data/PVR_TV.tif")) #load food production potential data and agricultural land quality data

PVR_TV.rs<-terra::resample(PVR_TV,new.ras, method="bilinear") #resample to 1km2 and reproject 
PVR_TV.p<-terra::project(PVR_TV.rs, "epsg:5070") 

PVR_TV.s<-PVR_TV.p #use for spatraster 

df_PVR<-as.data.frame(PVR_TV.s, xy=TRUE)

#plot food production potential 
PVRplot<-ggplot(df_PVR, aes(x = x, y = y, fill =PVR)) +
    geom_tile() +
    theme(
      panel.background =element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(limits=c(0,1))+
  labs(fill = "Food Production Potential")

#---------------------------------------#

#---------------------------------------#
#Agricultural Land Quality 
#Reclassify to get Low, medium, high Ag quantity (1/3 quantiles)
Quantile<-global(PVR_TV.s, fun=quantile, na.rm=TRUE)
AgQuality<-PVR_TV.s
reclass<-c(0,0.21,1, 0.21,0.49,2, 0.49,1,3)
reclass<-matrix(reclass, ncol=3, byrow=TRUE)

AgQuality.r<-classify(AgQuality, reclass, include.lowest=FALSE)

df_agquality<-as.data.frame(AgQuality.r, xy=TRUE)
df_agquality<-na.omit(df_agquality)

#plot agricultural land quality 
AgQualityPlot<-ggplot(df_agquality, aes(x = x, y = y, fill =PVR)) +
    geom_tile() +
    theme(
      panel.background =element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(limits=c(0,3))+
  labs(fill = "Agricultural Land Quality")

Ag_plots<-PVRplot+AgQualityPlot
#---------------------------------------#

#Agricultural land 
#----------------------------------------#
#Mask to measure total cultivated land protected 
mask.file<-"/Volumes/JodiBrandt/Common/SarahHalperin/Data/LandUse/TV_NLCD/NLCD_Weighted/TV.NLCD_2016w.tif"


#resample and project 

mask<-terra::rast(mask.file)

mask<-terra::resample(mask, new.ras, method="near")

mask<-terra::project(mask, "EPSG:5070")

#select ag land 
mask[is.nan(mask)]<-NA
mask[mask == 81]<-1
mask[mask == 82] <-1
mask[mask!=1]<-NA

#---------------------------------------#
#Ecosystem Services 
ES_List<-list.files(paste0(Folder, "Data/ES_Spatial_Layers"), pattern="*2016.tif", full.names=TRUE) #Bring in ES Data 

ES_rast<-lapply(ES_List, function (x){
    terra::rast(x)
})

ES_rast.p<-lapply(ES_rast, function (x){
  terra::project(x, crs(new.ras))
})

ES_rast1km<-lapply(ES_rast.p, function(x){
 terra::resample(x,new.ras, method="bilinear") #resample to 1km 
})


ES_rast1km.c<-lapply(ES_rast1km, function(x){
  terra::crop(x, PVR_TV.p)
}) #crop to PVR. 

ES_rast1km.c<-lapply(ES_rast1km.c, function(x){
  terra::mask(x, PVR_TV.p)
})#mask to PVR. Optimization restricted to areas that are agricultural land 

ES_rast1km.r<-lapply(ES_rast1km.c, function(x){
  raster::raster(x) #turn into raster 
})

```

```{r}
#------------------------------------#
# Plot ES inputs 
raster_list<-list(ES_rast1km.r[[1]], ES_rast1km.r[[3]], ES_rast1km.r[[4]], ES_rast1km.r[[6]]) 


# Create a vector of new layer names
layer_names_list <- c("CarbonSequestration", "HabitatQuality", "NitrogenRetention", "Recreation")

# Use a for loop to rename the layer names of each raster in the list
for (i in 1:length(raster_list)) {
  names(raster_list[[i]]) <- layer_names_list[[i]]
}

#plot carbon
  df.carbon <- as.data.frame(raster_list[[1]], xy = TRUE)
 df.carbon<-na.omit(df.carbon)
carbon<-ggplot(df.carbon, aes(x = x, y = y, fill =CarbonSequestration)) +
    geom_tile() +
    theme(
      panel.background = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(limits=c(3,15))+
  labs(fill = "Carbon Sequestration \n(Mg ha-1)")+
  theme(legend.margin = margin(0, 0, 0, 0))

#plot Habitat Quality 
 df.habitat <- as.data.frame(raster_list[[2]], xy = TRUE)
 df.habitat<-na.omit(df.habitat)
habitat<-ggplot(df.habitat, aes(x = x, y = y, fill =HabitatQuality)) +
    geom_tile() +
    theme(
      panel.background =element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(limits=c(0,1))+
  labs(fill = "Habitat Quality")
    
#plot Nitrogen 
 df.nitrogen <- as.data.frame(raster_list[[3]], xy = TRUE)
 df.nitrogen<-na.omit(df.nitrogen)
nitrogen<-ggplot(df.nitrogen, aes(x = x, y = y, fill =NitrogenRetention)) +
    geom_tile() +
    theme(
      panel.background =element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(limits=c(0,1))+
  labs(fill = "Nitrogen Retention\n(Proportion Nitrogen Load Retained)")

#plot Recreation
 df.recreation <- as.data.frame(raster_list[[4]], xy = TRUE)
 df.recreation<-na.omit(df.recreation)
recreation<-ggplot(df.recreation, aes(x = x, y = y, fill =Recreation)) +
    geom_tile() +
    theme(
      panel.background =element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis(name="Recreation", limits=c(0,1))


plot_list<-list(carbon, habitat, nitrogen, recreation)

plots <- lapply(plot_list, wrap_plots, nrow = 1)
reduce_plots <- wrap_plots(plots)
print(reduce_plots)

library(cowplot)
plotgrid<-plot_grid(carbon, habitat, nitrogen, recreation, ncol=2, align="hv")
#---------------------------------------#
```

```{r}
#https://datadryad.org/stash/dataset/doi:10.5061/dryad.np5hqbzq9
#---------------------------------------#
#Cost Data (Nolte 2020)
Cost_US<-terra::rast(paste0(Folder,"/Data/LandUse/cost_places/places_fmv_all.tif"))

Cost_US<-terra::project(Cost_US, "epsg:5070")

Cost_US<-terra::resample(Cost_US, new.ras, method="sum") #resample to 1km (should this be sum?)

#Crop to PVR
Cost_TV<-terra::crop(Cost_US, PVR_TV.p)
Cost_TV<-terra::mask(Cost_TV, PVR_TV.p)

#Cost_1km<-raster(Cost_TV)
cost<-Cost_TV

names(cost)<-"cost"

cost<-cost/10 #convert to million usd/1km 


#---------------------------------------#
#plot cost 
df.cost <- as.data.frame(cost, xy = TRUE)
#Plot cost data 
  cost.plot<-ggplot() +
    geom_tile(data=df.cost, aes(x = x, y = y, fill =cost)) +
    scale_fill_gradientn(name="USD / km²", colours = terrain.colors(10))+ 
    new_scale_fill()+
  geom_sf(data = StudyArea.sf, fill = NA, color = "black", size = 1) +
  theme(
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

```

```{r}
#---------------------------------------#
#Plot current cultivated land (mask)
df.mask<-as.data.frame(mask, xy=TRUE)
  mask.plot<-ggplot() +
    geom_tile(data=df.mask, aes(x = x, y = y, fill ="TV.NLCD_2016w")) +
    scale_fill_manual(values="#788f33", name="Current Agricultural Land", labels=c(""))+
  new_scale_fill()+
  geom_sf(data = StudyArea.sf, fill = NA, color = "black", size = 1) +
  theme(
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

```

```{r}
#-------------------------------------#
#Locked in/out layer (restrict optimization to unprotected lands)

Protected.area<-st_read(paste0(Folder, "Data/HabitatQuality_Data/GAP/PADUS2_1Designation_StateID.shp")) #protected lands data for idaho 

PA<-Protected.area %>%
  subset(Protected.area$GAP_Sts < "3")

PA.tv<-st_intersection(PA, StudyArea.sf)

PA.tv.p<-st_cast(PA.tv, "POLYGON") #needed to convert to polygon 

PA.tv.r<-rasterize(PA.tv.p, new.ras, "GAP_Sts")
values(PA.tv.r)[values(PA.tv.r) <= 2] <- 1


#locked.in<-PA.tv.r
locked.out<-PA.tv.r

#------------------------------------------#
#Plot protected areas 
df.PA<-as.data.frame(PA.tv.r, xy=TRUE)

PA.plot<-ggplot() +
  geom_tile(data=df.PA, aes(x = x, y = y, fill = "GAP_Sts")) +
    scale_fill_manual(values="#788f33", name="Current Protected Areas", labels=c(""))+
  new_scale_fill()+
  geom_sf(data = StudyArea.sf, fill = NA, color = "black", size = 1) +
  theme(
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

```

## Set targets

```{r}
#--------------------------------------#
#Set targets  
targets<-seq(0,0.4,0.05)
```

## Create ES Conservation Inputs

```{r}
#---------------------------------------#
#Create ES Conservation Inputs 
ES_inputs.pvr<-rast(list(ES_rast1km.c[[1]], ES_rast1km.c[[3]], ES_rast1km.c[[4]], ES_rast1km.c[[6]], PVR_TV.s))

#Carbon_inputs<-rast(list(ES_rast1km.c[[1]], PVR_TV.s))
Carbon_inputs<-rast(list(ES_rast1km.c[[1]]))

#Habitat_inputs<-rast(list(ES_rast1km.c[[3]], PVR_TV.s))
Habitat_inputs<-rast(list(ES_rast1km.c[[3]]))
#---------------------------------------#

```

## Solution ES problem

```{r}
set.seed(123)

# set cost of locked in areas to 0
cost[locked.out==1] <- 0

#

solutions <- generate_optim(inputs=ES_inputs.pvr, cost=cost, targets=targets, mask=mask,
                            locked.out = locked.out,
                            output.table=TRUE, output.rasters=TRUE,
                            table.columns = c("total_cost","percent_ES_protected","total_pixels","percent_mask_pixels_in_solution"))


solution30<-solutions[[2]][[7]]
solution30[solution30 ==0]<-NA

#writeRaster(solution30, paste0(Folder, "Chapter3/SolutionRasters/Solution_CombinedScenario.tif"), overwrite=TRUE)

sol.table <- solutions[[1]]

# Table modifications
sol.table$cost_bil <- sol.table$total_cost/1000
sol.table[,stringr::str_which(names(sol.table),"target")] <- sol.table[,stringr::str_which(names(sol.table),"target")]*100
sol.table$total_pixels_mask <- sol.table$percent_mask_pixels_in_solution/100 * subset(freq(mask), freq(mask)[,"value"]==1)[,"count"]


#write.csv(sol.table, paste0(Folder,"Chapter3/OutputTables/SolTableCombined.csv"))

```

## Solution PVR Problem

```{r}
# set cost of locked out areas to 0
cost[locked.out==1] <- 0

#
solutions.pvr <- generate_optim(inputs=PVR_TV.s, cost=cost, targets=targets, mask=mask,
                            locked.out=locked.out,
                            output.table=TRUE, output.rasters=TRUE,
                            table.columns = c("total_cost","percent_ES_protected","total_pixels","percent_mask_pixels_in_solution"))


solution30.pvr<-solutions.pvr[[2]][[7]]
solution30.pvr[solution30.pvr ==0]<-NA

#writeRaster(solution30.pvr, paste0(Folder, "Chapter3/SolutionRasters/Solution_AgScenario.tif"), overwrite=TRUE)



sol.table.pvr <- solutions.pvr[[1]]

# Table modifications
sol.table.pvr$cost_bil <- sol.table.pvr$total_cost/1000
sol.table.pvr[,stringr::str_which(names(sol.table.pvr),"target")] <- sol.table.pvr[,stringr::str_which(names(sol.table.pvr),"target")]*100
sol.table.pvr$total_pixels_mask <- sol.table.pvr$percent_mask_pixels_in_solution/100 * subset(freq(mask), freq(mask)[,"value"]==1)[,"count"]

#write.csv(sol.table.pvr, paste0(Folder,"Chapter3/OutputTables/SolTableAG.csv"))
```

## Solution Climate Problem

```{r}
#
solutions.carbon <- generate_optim(inputs=Carbon_inputs, cost=cost, targets=targets, mask=mask,
                            locked.out=locked.out,
                            output.table=TRUE, output.rasters=TRUE,
                            table.columns = c("total_cost","percent_ES_protected","total_pixels","percent_mask_pixels_in_solution"))

solution30.carbon<-solutions.carbon[[2]][[7]]
solution30.carbon[solution30.carbon ==0]<-NA

#writeRaster(solution30.carbon, paste0(Folder, "Chapter3/SolutionRasters/Solution_ClimateScenario.tif"), overwrite=TRUE)

sol.table.carbon <- solutions.carbon[[1]]

# Table modifications
sol.table.carbon$cost_bil <- sol.table.carbon$total_cost/1000
sol.table.carbon[,stringr::str_which(names(sol.table.carbon),"target")] <- sol.table.carbon[,stringr::str_which(names(sol.table.carbon),"target")]*100
sol.table.carbon$total_pixels_mask <- sol.table.carbon$percent_mask_pixels_in_solution/100 * subset(freq(mask), freq(mask)[,"value"]==1)[,"count"]

#write.csv(sol.table.carbon, paste0(Folder,"Chapter3/OutputTables/SolTableCarbon.csv"))

```

## Solution Habitat Problem

```{r}
#
solutions.habitat <- generate_optim(inputs=Habitat_inputs, cost=cost, targets=targets, mask=mask,
                            locked.out=locked.out,
                            output.table=TRUE, output.rasters=TRUE,
                            table.columns = c("total_cost","percent_ES_protected","total_pixels","percent_mask_pixels_in_solution"))

solution30.habitat<-solutions.habitat[[2]][[7]]
solution30.habitat[solution30.habitat ==0]<-NA

#writeRaster(solution30.habitat, paste0(Folder, "Chapter3/SolutionRasters/Solution_HabitatScenario.tif"), overwrite=TRUE)

sol.table.habitat <- solutions.habitat[[1]]

# Table modifications
sol.table.habitat$cost_bil <- sol.table.habitat$total_cost/1000
sol.table.habitat[,stringr::str_which(names(sol.table.habitat),"target")] <- sol.table.habitat[,stringr::str_which(names(sol.table.habitat),"target")]*100
sol.table.habitat$total_pixels_mask <- sol.table.habitat$percent_mask_pixels_in_solution/100 * subset(freq(mask), freq(mask)[,"value"]==1)[,"count"]

#write.csv(sol.table.habitat, paste0(Folder,"Chapter3/OutputTables/SolTableHabitat.csv"))
```

## Bar graph total cultivated land for each solution

```{r}
sol.table.pvr.30 <-sol.table.pvr %>%
  filter(target == "30")
sol.table.30 <-sol.table %>%
  filter(target == "30")
sol.table.carbon.30 <-sol.table.carbon %>%
  filter(target == "30")
sol.table.habitat.30 <-sol.table.habitat %>%
  filter(target == "30")

df.totalag<-as.data.frame(cbind(sol.table.pvr.30$percent_mask_pixels_in_solution, sol.table.30$percent_mask_pixels_in_solution, sol.table.carbon.30$percent_mask_pixels_in_solution, sol.table.habitat.30$percent_mask_pixels_in_solution))

df.totalag<-as.data.frame(t(na.omit(df.totalag)))
df.totalag$Scenario<-c("Agricultural Productivity", "Combined Ecosystem Services", "Climate Adaptation", "Wildlife Habitat")
colnames(df.totalag)<-c("Percent", "Scenario")

df.totalag$Scenario<-factor(df.totalag$Scenario, levels=c("Agricultural Productivity", "Climate Adaptation", "Wildlife Habitat", "Combined Ecosystem Services"))

#Plot Percent cultivated Land 
AgLand<-ggplot(df.totalag, aes(x = Scenario)) +
  geom_bar(aes(y = Percent), stat = "identity", position = "dodge", fill="#aeac4c") +
  labs(x = "Protection Scenario", y = "Percent Agricultural Land (%)") +
  theme_classic()+
    theme(
    axis.text = element_text(size = 12),  # Adjust the font size for tick labels
    axis.title = element_text(size = 14)  # Adjust the font size for axis titles
  )
```

## Calculate Cost

```{r}
df.cost<-as.data.frame(cbind( sol.table.pvr$cost_bil, sol.table$cost_bil,sol.table.carbon$cost_bil, sol.table.habitat$cost_bil))

colnames(df.cost)<-c("Agricultural Productivity","Combined Ecosystem Services", "Climate", "Wildlife Habitat")
df.cost$Target<-c(0,5,10,15,20,25,30,35,40)

df.cost.melt<-melt(df.cost, id="Target")


#Plot cost 
Costplot<-ggplot(df.cost.melt) +
  geom_line(aes(x=Target, y=value, color=variable)) +
  geom_point(aes(x=Target, y=value, color=variable)) +
   scale_x_continuous(name="Protection Target (%)", breaks=seq(0,40,5)) +
  scale_y_continuous(name="Total Cost (billion USD)", breaks=seq(0,5,0.5))+
  labs(colour = "Protection Scenario")+
  geom_vline(xintercept = 30, linetype = "dashed", color = "black")+
  scale_color_viridis_d()+
  theme_classic()+
  theme(
    axis.text = element_text(size = 12),   # Adjust the font size for tick labels
    axis.title = element_text(size = 14)   # Adjust the font size for axis titles
  )

```

## Calculate Agricultural Land Quality Percent

```{r}
#---------------------------------------#
solutions.r<-lapply(solutions[[2]], function(x){ 
                    raster::raster(x)
  }) 

solutions.pvr.r<-lapply(solutions.pvr[[2]], function(x){ 
                    raster::raster(x)
  }) 

solutions.carbon.r<-lapply(solutions.carbon[[2]], function(x){ 
                    raster::raster(x)
  }) 

solutions.habitat.r<-lapply(solutions.habitat[[2]], function(x){ 
                    raster::raster(x)
  }) 

#----------------------------------------------------#
AgQuality.r<-raster::raster(AgQuality.r)

stack.ES<-stack(solutions.r)
stack.pvr<-stack(solutions.pvr.r)
stack.carbon<-stack(solutions.carbon.r)
stack.habitat<-stack(solutions.habitat.r)


stack.q<-stack(stack.ES, stack.pvr,stack.carbon,stack.habitat, AgQuality.r)
df.q<-as.data.frame(na.omit(values(stack.q))) 

Tot.pix<-t(df.q[1:36] %>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))))
variable <- rownames(Tot.pix)
  rownames(Tot.pix) <- NULL
  Tot.pix <- as.data.frame(cbind(Tot.pix,variable))

df.q.melt<-melt(df.q, id="PVR")
df.q.aggregate<-aggregate(value ~ PVR + variable, data=df.q.melt, FUN=sum)

df.q.aggregate<-left_join(df.q.aggregate, Tot.pix, by="variable")
df.q.aggregate$Perc_Quality<-df.q.aggregate$value/as.numeric(df.q.aggregate$V1)*100

df.quality.combined<-na.omit(df.q.aggregate[c(1,2,5)])
colnames(df.quality.combined)<-c("Quality", "Target", "Perc_Quality")

df.quality.combined<-df.quality.combined %>%
  mutate(Target=recode(Target, 
                       'cost.2.1'="Combined 5%",
                       'cost.3.1'="Combined 10%",
                       'cost.4.1' = "Combined 15%", 
                       'cost.5.1' = "Combined 20%", 
                       'cost.6.1' ="Combined 25%",
                       'cost.7.1' ="Combined 30%",
                       'cost.8.1'="Combined 35%", 
                       'cost.9.1'="Combined 40%", 
                        'cost.2.2'="PVR 5%",
                       'cost.3.2'="PVR 10%",
                       'cost.4.2' = "PVR 15%", 
                       'cost.5.2' = "PVR 20%", 
                       'cost.6.2' ="PVR 25%",
                       'cost.7.2' ="PVR 30%",
                       'cost.8.2'="PVR 35%", 
                       'cost.9.2'="PVR 40%", 
                        'cost.2.3'="Carbon 5%",
                       'cost.3.3'="Carbon 10%",
                       'cost.4.3' = "Carbon 15%", 
                       'cost.5.3' = "Carbon 20%", 
                       'cost.6.3' ="Carbon 25%",
                       'cost.7.3' ="Carbon 30%",
                       'cost.8.3'="Carbon 35%", 
                       'cost.9.3'="Carbon 40%", 
                        'cost.2.4'="Habitat 5%",
                       'cost.3.4'="Habitat 10%",
                       'cost.4.4' = "Habitat 15%", 
                       'cost.5.4' = "Habitat 20%", 
                       'cost.6.4' ="Habitat 25%",
                       'cost.7.4' ="Habitat 30%",
                       'cost.8.4'="Habitat 35%", 
                       'cost.9.4'="Habitat 40%")) %>%
  mutate(Quality=recode(Quality, 
                        '1'="Low", 
                        '2'="Medium",
                        '3'="High")) %>%
  mutate(Perc_Quality=round(Perc_Quality, digits=2))

write.csv(df.quality.combined, paste0(Folder,"Chapter3/OutputTables/SolutionAgQuality.csv"))

#---------------------------------------#
```

## Agricultural Land Quality Bar Graphs

```{r}
library(stringr)
df.quality.30<- df.quality.combined %>%
  filter(str_ends(Target, "30%"))

# Reorder the "Quality" variable
df.quality.30$Quality <- factor(df.quality.30$Quality, levels = c("Low", "Medium", "High"))

df.quality.30$Target <-factor(df.quality.30$Target, levels=c("PVR 30%", "Carbon 30%", "Habitat 30%","Combined 30%"))

new_labels <- c("Agricultural Productivity", "Climate Adaptation", "Wildlife Habitat", "Combined Ecosystem Services")

# Plot with modified x-axis labels

Quality<-ggplot(df.quality.30, aes(x = Target, fill = Quality)) +
  geom_bar(aes(y = Perc_Quality), stat = "identity", position = "dodge") +
  labs(x = "Protection Scenario", y = "Percent Protected at 30% Targets (%)", fill = "Agricultural Land Quality") +
  scale_fill_manual(values = c("#aeac4c","#788f33","#165d43")) +
  scale_x_discrete(labels = new_labels) + # Setting custom x-axis labels
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    theme(
    axis.text = element_text(size = 12),   # Adjust the font size for tick labels
    axis.title = element_text(size = 14)   # Adjust the font size for axis titles
  )

  

plotAG<-plot_grid(AgLand,Quality, ncol=2, align="h")
```

## Ecosystem Services Percent 

```{r}
#Combined ES Scenario 
ES <- data.frame(perc_protected=unlist(sol.table[,stringr::str_which(names(sol.table),"percent_ES")]),
                 target=unlist(sol.table[,stringr::str_which(names(sol.table),"target")]),
                 ES=stringr::str_extract(names(unlist(sol.table[,stringr::str_which(names(sol.table),"percent_ES")])), pattern="[:digit:]"),
                 cost=sol.table$cost_bil,
                 run.num=1:nrow(sol.table))
df.aggregate.ES<-ES %>%
  mutate(ES=recode(ES, 
                        '1'="Carbon Sequestration", 
                        '2'="Habitat Quality",
                        '3'="Nitrogen Retention", 
                        '4' = "Recreation", 
                        '5' = "PVR"))

#write.csv(df.aggregate.ES, paste0(Folder,"Chapter3/OutputTables/ESpercent_combined.csv"))
```

```{r}
#PVR Scenario 
ES.rasters<-stack(ES_rast1km.r[[1]], ES_rast1km.r[[3]], ES_rast1km.r[[4]], ES_rast1km.r[[6]])
stack.pvr.ES<-stack(stack.pvr, ES.rasters)
df.pvr.ES<-as.data.frame(na.omit(values(stack.pvr.ES))) 

Tot.ES<-t(df.pvr.ES[10:13] %>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))))
variable <- rownames(Tot.ES)
  rownames(Tot.ES) <- NULL
  Tot.ES<- as.data.frame(cbind(Tot.ES,variable))

df.pvr.ES.melt<-melt(df.pvr.ES, id=c("tot_c_fut_weight", "reten_ratio", "quality_f_02", "X02_recreation_2016sum"))
df.pvr.ES.melt<-df.pvr.ES.melt %>%
  filter(value == 1)

df.pvr.ES.melt<-melt(df.pvr.ES.melt, id="variable")
colnames(df.pvr.ES.melt)<-c("solution", "variable", "value")

df.aggregate.pvr.ES<-aggregate(value ~ variable + solution, data=df.pvr.ES.melt, FUN=sum)

df.aggregate.pvr.ES<-left_join(df.aggregate.pvr.ES, Tot.ES, by="variable")
df.aggregate.pvr.ES$Perc_ES<-df.aggregate.pvr.ES$value/as.numeric(df.aggregate.pvr.ES$V1)*100
df.aggregate.pvr.ES<-na.omit(df.aggregate.pvr.ES)

df.aggregate.pvr.ES<-df.aggregate.pvr.ES %>%
  mutate(solution=recode(solution, 
                        'cost.2'="5%", 
                        'cost.3'="10%",
                        'cost.4'="15%", 
                        'cost.5' = "20%", 
                        'cost.6' = "25%",
                        'cost.7'= "30%", 
                        'cost.8'= "35%",
                        'cost.9'="40%"))

write.csv(df.aggregate.pvr.ES, paste0(Folder,"Chapter3/OutputTables/ESpercent_agriculture.csv"))



```

```{r}
#Climate Scenario 
ES.carbon.rasters<-stack(ES_rast1km.r[[1]], ES_rast1km.r[[3]], ES_rast1km.r[[4]], ES_rast1km.r[[6]], raster(PVR_TV.s))
stack.carbon.ES<-stack(stack.carbon, ES.carbon.rasters)
df.carbon.ES<-as.data.frame(na.omit(values(stack.carbon.ES))) 

Tot.carbon.ES<-t(df.carbon.ES[10:14] %>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))))
variable <- rownames(Tot.carbon.ES)
  rownames(Tot.carbon.ES) <- NULL
  Tot.carbon.ES<- as.data.frame(cbind(Tot.carbon.ES,variable))

df.carbon.ES.melt<-melt(df.carbon.ES, id=c("tot_c_fut_weight", "reten_ratio", "quality_f_02", "X02_recreation_2016sum", "PVR"))
df.carbon.ES.melt<-df.carbon.ES.melt %>%
  filter(value == 1)

df.carbon.ES.melt<-melt(df.carbon.ES.melt, id="variable")
colnames(df.carbon.ES.melt)<-c("solution", "variable", "value")

df.aggregate.carbon.ES<-aggregate(value ~ variable + solution, data=df.carbon.ES.melt, FUN=sum)

df.aggregate.carbon.ES<-left_join(df.aggregate.carbon.ES, Tot.carbon.ES, by="variable")
df.aggregate.carbon.ES$Perc_ES<-df.aggregate.carbon.ES$value/as.numeric(df.aggregate.carbon.ES$V1)*100
df.aggregate.carbon.ES<-na.omit(df.aggregate.carbon.ES)

df.aggregate.carbon.ES<-df.aggregate.carbon.ES %>%
  mutate(solution=recode(solution, 
                        'cost.2'="5%", 
                        'cost.3'="10%",
                        'cost.4'="15%", 
                        'cost.5' = "20%", 
                        'cost.6' = "25%",
                        'cost.7'= "30%", 
                        'cost.8'= "35%",
                        'cost.9'="40%"))

#write.csv(df.aggregate.carbon.ES, paste0(Folder,"Chapter3/OutputTables/ESpercent_climate.csv"))
```

```{r}
#Wildlife Habitat Scenario 
ES.habitat.rasters<-stack(ES_rast1km.r[[1]], ES_rast1km.r[[3]], ES_rast1km.r[[4]], ES_rast1km.r[[6]], raster(PVR_TV.s))
stack.habitat.ES<-stack(stack.habitat, ES.habitat.rasters)
df.habitat.ES<-as.data.frame(na.omit(values(stack.habitat.ES))) 

Tot.habitat.ES<-t(df.habitat.ES[10:14] %>%
    summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))))
variable <- rownames(Tot.habitat.ES)
  rownames(Tot.habitat.ES) <- NULL
  Tot.habitat.ES<- as.data.frame(cbind(Tot.habitat.ES,variable))

df.habitat.ES.melt<-melt(df.habitat.ES, id=c("tot_c_fut_weight", "reten_ratio", "quality_f_02", "X02_recreation_2016sum", "PVR"))
df.habitat.ES.melt<-df.habitat.ES.melt %>%
  filter(value == 1)

df.habitat.ES.melt<-melt(df.habitat.ES.melt, id="variable")
colnames(df.habitat.ES.melt)<-c("solution", "variable", "value")

df.aggregate.habitat.ES<-aggregate(value ~ variable + solution, data=df.habitat.ES.melt, FUN=sum)

df.aggregate.habitat.ES<-left_join(df.aggregate.habitat.ES, Tot.habitat.ES, by="variable")
df.aggregate.habitat.ES$Perc_ES<-df.aggregate.habitat.ES$value/as.numeric(df.aggregate.habitat.ES$V1)*100
df.aggregate.habitat.ES<-na.omit(df.aggregate.habitat.ES)

df.aggregate.habitat.ES<-df.aggregate.habitat.ES %>%
  mutate(solution=recode(solution, 
                        'cost.2'="5%", 
                        'cost.3'="10%",
                        'cost.4'="15%", 
                        'cost.5' = "20%", 
                        'cost.6' = "25%",
                        'cost.7'= "30%", 
                        'cost.8'= "35%",
                        'cost.9'="40%"))

#write.csv(df.aggregate.habitat.ES, paste0(Folder,"Chapter3/OutputTables/ESpercent_habitat.csv")) 
```

## Solution Maps

```{r}
#---------------------------------------------------#
#ES Solution 
#Select solution to plot and turn into raster 
solutions.ES.30<-raster::raster(solutions[[2]][[7]])
   
#convert to dataframe
df.solutions.ES.30<-as.data.frame(solutions.ES.30, xy=TRUE)
colnames(df.solutions.ES.30)<-c("x","y", "value") 
df.solutions.ES.30$value<-as.factor(df.solutions.ES.30$value)


df.solutions.ES.30<-na.omit(df.solutions.ES.30)
  

#convert locked.out to dataframe
df.locked.out<-as.data.frame(raster::raster(locked.out), xy=TRUE) %>%
  na.omit()
df.locked.out$GAP_Sts<-as.factor(df.locked.out$GAP_Sts)


ES_solution<-ggplot()+
  geom_tile(data=df.solutions.ES.30, 
              aes(x=x, y=y, 
                  fill=value))+
  scale_fill_manual(values= c("gray","#788f33"), name="Priority Area", labels=c("Not Selected", "Selected")) +
  new_scale_fill()+
  geom_tile(data=df.locked.out, aes(x=x, y=y, fill="Gap_Sts"))+
  scale_fill_manual(values="#aeac4c", name="Current Protected Area", labels=c(""))+
  geom_sf(data=StudyArea.sf, fill=NA, color="black", linewidth=1)+
  ggtitle("Combined Ecosystem Services")+
  theme_void()+
  theme(panel.border = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())
#---------------------------------------------------#

#----------------------------------------------------#

#PVR 
solutions.pvr.30<-raster::raster(solutions.pvr[[2]][[7]])


#convert to dataframe
df.pvr.30<-as.data.frame(solutions.pvr.30, xy=TRUE)
colnames(df.pvr.30)<-c("x","y", "value") 
df.pvr.30$value<-as.factor(df.pvr.30$value)


df.pvr.30<-na.omit(df.pvr.30)

PVR_solution<-ggplot()+
  geom_tile(data=df.pvr.30, 
              aes(x=x, y=y, 
                  fill=value))+
  scale_fill_manual(values= c("gray","#788f33"), name="Priority Area", labels=c("Not Selected", "Selected")) +
  new_scale_fill()+
  geom_tile(data=df.locked.out, aes(x=x, y=y, fill="Gap_Sts"))+
  scale_fill_manual(values="#aeac4c", name="Current Protected Area", labels=c(""))+
  geom_sf(data=StudyArea.sf, fill=NA, color="black", linewidth=1)+
  ggtitle("Agricultural Productivity")+
  theme_void()+
  theme(panel.border = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())
#---------------------------------------------------#


#---------------------------------------------------#
#Carbon Solution 
solutions.carbon.30<-raster::raster(solutions.carbon[[2]][[7]])

#convert to dataframe
df.carbon.30<-as.data.frame(solutions.carbon.30, xy=TRUE)
colnames(df.carbon.30)<-c("x","y", "value") 
df.carbon.30$value<-as.factor(df.carbon.30$value)


df.carbon.30<-na.omit(df.carbon.30)

Carbon_solution<-ggplot()+
  geom_tile(data=df.carbon.30, 
              aes(x=x, y=y, 
                  fill=value))+
  scale_fill_manual(values= c("gray","#788f33"), name="Priority Area", labels=c("Not Selected", "Selected")) +
  new_scale_fill()+
  geom_tile(data=df.locked.out, aes(x=x, y=y, fill="Gap_Sts"))+
  scale_fill_manual(values="#aeac4c", name="Current Protected Area", labels=c(""))+
  geom_sf(data=StudyArea.sf, fill=NA, color="black", linewidth=1)+
  ggtitle("Climate Adaptation")+
  theme_void()+
  theme(panel.border = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())
#----------------------------------------------------#

#---------------------------------------------------#
#Habitat Solution 
solutions.habitat.30<-raster::raster(solutions.habitat[[2]][[7]])

#convert to dataframe
df.habitat.30<-as.data.frame(solutions.habitat.30, xy=TRUE)
colnames(df.habitat.30)<-c("x","y", "value") 
df.habitat.30$value<-as.factor(df.habitat.30$value)


df.habitat.30<-na.omit(df.habitat.30)

Habitat_solution<-ggplot()+
  geom_tile(data=df.habitat.30, 
              aes(x=x, y=y, 
                  fill=value))+
  scale_fill_manual(values= c("gray","#788f33"), name="Priority Area", labels=c("Not Selected", "Selected")) +
  new_scale_fill()+
  geom_tile(data=df.locked.out, aes(x=x, y=y, fill="Gap_Sts"))+
  scale_fill_manual(values="#aeac4c", name="Current Protected Area", labels=c(""))+
  geom_sf(data=StudyArea.sf, fill=NA, color="black", linewidth=1)+
  ggtitle("Wildlife Habitat")+
  theme_void()+
  theme(panel.border = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())
#---------------------------------------------------#
#Overlapping pixels 
overlap<-solutions.habitat.30+solutions.carbon.30+solutions.pvr.30+solutions.ES.30

#convert to dataframe
df.overlap<-as.data.frame(overlap, xy=TRUE)
colnames(df.overlap)<-c("x","y", "value") 
df.overlap$value<-as.factor(df.overlap$value)


df.overlap<-na.omit(df.overlap)


overlap<-ggplot()+
  geom_tile(data=df.overlap, 
              aes(x=x, y=y, 
                  fill=value))+
  scale_fill_manual(values= c("gray","#414487FF", "#2A788EFF","#7AD151FF", "#FDE725FF"), name="Priority Area", labels=c("Not Selected", "Selected in 1 Scenario", "Selected in 2 Scenarios", "Selected in 3 Scenarios", "Selected in ALL Scenarios")) +
  new_scale_fill()+
  geom_tile(data=df.locked.out, aes(x=x, y=y, fill="Gap_Sts"))+
  scale_fill_manual(values="#aeac4c", name="Current Protected Area", labels=c(""))+
  geom_sf(data=StudyArea.sf, fill=NA, color="black", linewidth=1)+
  ggtitle("Overlap Between")+
  theme_void()+
  theme(panel.border = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

library(patchwork)
Solutions<-PVR_solution+Carbon_solution+Habitat_solution+ES_solution+overlap
```

## Combined Biodiversity and Climate Index

Suraci JP, Farwell LS, Littlefield CE, Freeman PT,  Zachmann LJ, Landau VA, Anderson JJ, Dickson BG. 2023. Achieving conservation targets by jointly addressing climate change and biodiversity loss. *Ecosphere*

https://figshare.com/articles/dataset/Data_from_Suraci_et_al_2023_Ecosphere/22197592/1?file=39450403

```{r}
#Load Data 
combined_index<-terra::rast(paste0(Folder, "Data/Suraci2023/conus-combined-index.tif"))

combined_index<-terra::project(combined_index, new.ras)

combined_index.tv<-terra::crop(combined_index, StudyArea.sf)
combined_index.tv<-terra::mask(combined_index.tv, StudyArea.sf)


Quantile_combined.i<-global(combined_index.tv, fun=quantile, na.rm=TRUE) # >-1.82

#Combined ES Scenario 
solutions.ES.30[solutions.ES.30!=1]<-NA

solutions.ES.30.p<-rasterToPolygons(solutions.ES.30, dissolve=TRUE) #convert to polygon
solutions.ES.30.p<-vect(solutions.ES.30.p) #convert to spatvector 

combined.solutions.30<-terra::extract(combined_index.tv, solutions.ES.30.p)
colnames(combined.solutions.30)<-c("Pixel","combined_index")

combined.hv<-combined.solutions.30 %>%
  filter(combined_index > -1.82)


average_combined<-mean(combined.solutions.30$combined_index)# average index value 

ES.combined.sum<-sum(combined.hv$Pixel)/sum(combined.solutions.30$Pixel)*100 #10.40% or 70 pixels 

#PVR Scenario
solutions.pvr.30[solutions.pvr.30!=1]<-NA
solutions.pvr.30.p<-rasterToPolygons(solutions.pvr.30, dissolve=TRUE) #convert to polygon
solutions.pvr.30.p<-vect(solutions.pvr.30.p) #convert to spatvector 

combined.pvr.solutions.30<-terra::extract(combined_index.tv, solutions.pvr.30.p)
colnames(combined.pvr.solutions.30)<-c("Pixel","combined_index")


combined.pvr.hv<-combined.pvr.solutions.30 %>%
  filter(combined_index > -1.82)

pvr.average_combined<-mean(combined.pvr.solutions.30$combined_index)

pvr.combined.sum<-sum(combined.pvr.hv$Pixel)/sum(combined.pvr.solutions.30$Pixel)*100 #0% or 0 pixels 

#Climate Scenario
solutions.carbon.30[solutions.carbon.30!=1]<-NA
solutions.climate.30.p<-rasterToPolygons(solutions.carbon.30, dissolve=TRUE) #convert to polygon
solutions.climate.30.p<-vect(solutions.climate.30.p) #convert to spatvector 

combined.climate.solutions.30<-terra::extract(combined_index.tv, solutions.climate.30.p)
colnames(combined.climate.solutions.30)<-c("Pixel","combined_index")

combined.climate.hv<-combined.climate.solutions.30 %>%
  filter(combined_index > -1.82)

climate.combined.sum<-sum(combined.climate.hv$Pixel)/sum(combined.climate.solutions.30$Pixel)*100 #10.34% or 69 pixels 

climate.average_combined<-mean(combined.climate.solutions.30$combined_index)


#Habitat 
solutions.habitat.30[solutions.habitat.30!=1]<-NA
solutions.habitat.30.p<-rasterToPolygons(solutions.habitat.30, dissolve=TRUE) #convert to polygon
solutions.habitat.30.p<-vect(solutions.habitat.30.p) #convert to spatvector 

combined.habitat.solutions.30<-terra::extract(combined_index.tv, solutions.habitat.30.p)
colnames(combined.habitat.solutions.30)<-c("Pixel","combined_index")

habitat.average_combined<-mean(combined.habitat.solutions.30$combined_index)

combined.habitat.hv<-combined.habitat.solutions.30 %>%
  filter(combined_index > -1.82)

habitat.combined.sum<-sum(combined.habitat.hv$Pixel)/sum(combined.habitat.solutions.30$Pixel)*100 #15.40% or 95 pixels 

habitat.combined.pixel<-sum(combined.habitat.hv$Pixel)


```

## Climate Index

```{r}
climate_index<-terra::rast(paste0(Folder, "Data/Suraci2023/conus-climate-index.tif"))

climate_index<-terra::project(climate_index, new.ras)

climate_index.tv<-terra::crop(climate_index, StudyArea.sf)
climate_index.tv<-terra::mask(climate_index.tv, StudyArea.sf)

Quantile_climate.i<-global(climate_index.tv, fun=quantile, na.rm=TRUE) # >-1.79

#Combined ES Scenario 
climate.solutions.30<-terra::extract(climate_index.tv, solutions.ES.30.p)
colnames(climate.solutions.30)<-c("Pixel","combined_index")

average_climate<-mean(climate.solutions.30$combined_index)

climate.combined.hv<-climate.solutions.30 %>%
  filter(combined_index > -1.79)

sum(climate.combined.hv$Pixel)/sum(climate.solutions.30$Pixel)*100 #18.7% or 126 pixels 

#PVR Scenario

climate.pvr.solutions.30<-terra::extract(climate_index.tv, solutions.pvr.30.p)
colnames(climate.pvr.solutions.30)<-c("Pixel","combined_index")

pvr.average_climate<-mean(climate.pvr.solutions.30$combined_index)

climate.pvr.hv<-climate.pvr.solutions.30 %>%
  filter(combined_index > -1.79)

sum(climate.pvr.hv$Pixel)/sum(climate.pvr.solutions.30$Pixel)*100 #13.41 or 61 pixels 

#Climate Scenario
climate.climate.solutions.30<-terra::extract(climate_index.tv, solutions.climate.30.p)
colnames(climate.climate.solutions.30)<-c("Pixel","combined_index")

carbon.average_climate<-mean(climate.climate.solutions.30$combined_index)

climate.climate.hv<-climate.climate.solutions.30 %>%
  filter(combined_index > -1.79)

sum(climate.climate.hv$Pixel)/sum(climate.climate.solutions.30$Pixel)*100 #24.59 or 164 pixels 

#Habitat 

climate.habitat.solutions.30<-terra::extract(climate_index.tv, solutions.habitat.30.p)
colnames(climate.habitat.solutions.30)<-c("Pixel","combined_index")

habitat.average_climate<-mean(climate.habitat.solutions.30$combined_index)

climate.habitat.hv<-climate.habitat.solutions.30 %>%
  filter(combined_index > -1.79)

sum(climate.habitat.hv$Pixel)/sum(climate.habitat.solutions.30$Pixel)*100 #21.72 or 134
```

## Biodiversity Index

```{r}
biodiversity_index<-terra::rast(paste0(Folder, "Data/Suraci2023/conus-biodiversity-index.tif"))

biodiversity_index<-terra::project(biodiversity_index, new.ras)

biodiversity_index.tv<-terra::crop(biodiversity_index, StudyArea.sf)
biodiversity_index.tv<-terra::mask(biodiversity_index.tv, StudyArea.sf)

Quantile_biodiversity.i<-global(biodiversity_index.tv, fun=quantile, na.rm=TRUE) # >-0.34

#Combined ES Scenario 
biodiversity.solutions.30<-terra::extract(biodiversity_index.tv, solutions.ES.30.p)
colnames(biodiversity.solutions.30)<-c("Pixel","combined_index")

average_biodiversity<-mean(biodiversity.solutions.30$combined_index)

biodiversity.hv<-biodiversity.solutions.30 %>%
  filter(combined_index > -0.34)

sum(biodiversity.hv$Pixel)/sum(biodiversity.solutions.30$Pixel)*100 #17.09 or 115

#PVR Scenario

biodiversity.pvr.solutions.30<-terra::extract(biodiversity_index.tv, solutions.pvr.30.p)
colnames(biodiversity.pvr.solutions.30)<-c("Pixel","combined_index")

pvr.average_biodiversity<-mean(biodiversity.pvr.solutions.30$combined_index)

biodiversity.pvr.hv<-biodiversity.pvr.solutions.30 %>%
  filter(combined_index > -0.34)

sum(biodiversity.pvr.hv$Pixel)/sum(biodiversity.pvr.solutions.30$Pixel)*100 #0 or 0 

#Climate Scenario
biodiversity.climate.solutions.30<-terra::extract(biodiversity_index.tv, solutions.climate.30.p)
colnames(biodiversity.climate.solutions.30)<-c("Pixel","combined_index")

carbon.average_biodiversity<-mean(biodiversity.climate.solutions.30$combined_index)

biodiversity.climate.hv<-biodiversity.climate.solutions.30 %>%
  filter(combined_index > -0.34)

sum(biodiversity.climate.hv$Pixel)/sum(biodiversity.climate.solutions.30$Pixel)*100 #16.49 or 110 

#Habitat 

biodiversity.habitat.solutions.30<-terra::extract(biodiversity_index.tv, solutions.habitat.30.p)
colnames(biodiversity.habitat.solutions.30)<-c("Pixel","combined_index")

habitat.average_biodiversity<-mean(biodiversity.habitat.solutions.30$combined_index)

biodiversity.habitat.hv<-biodiversity.habitat.solutions.30 %>%
  filter(combined_index > -0.34)

sum(biodiversity.habitat.hv$Pixel)/sum(biodiversity.habitat.solutions.30$Pixel)*100 #21.56 or 133
```

## INDEX plots

```{r}
index_rasters<-list(combined_index.tv, climate_index.tv, biodiversity_index.tv)

# Create a vector of new layer names
index_names_list <- c("Combined", "Climate", "Biodiversity")

# Use a for loop to rename the layer names of each raster in the list
for (i in 1:length(index_rasters)) {
  names(index_rasters[[i]]) <- index_names_list[[i]]
}


# Function to plot a raster using ggplot with specified layer name
plot_raster <- function(raster, layer_names, study_area) {
  df <- as.data.frame(raster, xy = TRUE)
  theme_set(theme_void())  # Override default theme settings
  ggplot() +
    geom_raster(data=df, aes(x = x, y = y, fill = .data[[layer_names]])) +
    geom_sf(data = study_area, fill = NA, color = "black", size = 2) +  # Add the geom_sf layer
    theme(
      panel.background = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    ) +
    scale_fill_viridis()
}

# Plot each raster with different layer names using a for loop
plot_list <- list()
for (i in 1:length(index_rasters)) {
  raster <- index_rasters[[i]]
  layer_names <- index_names_list[[i]]
  
  raster_plots <- list()
  for (j in 1:length(layer_names)) {
    layer_name <- layer_names[j]
    raster_plots[[j]] <- plot_raster(raster, layer_name, StudyArea.sf)  # Pass StudyArea.sf as an argument
  }
  
  plot_list[[i]] <- raster_plots
}

plots.index <- lapply(plot_list, wrap_plots, nrow = 1)
index_plots <- wrap_plots(plots.index)
print(index_plots) 
```

##  Bar graphs for index values

```{r}
Scenario<-c("Agricultural Productivity", "Climate Adaptation", "Wildlife Habitat", "Combined Ecosystem Services")

#these numbers are taken from caluclations done above under each index 
Percent.combined<-c(0,10.34,15.4,10.4)
Percent.climate<-c(13.41,24.59, 21.72, 18.7)
Percent.biodiversity<-c(0, 16.49, 21.56,17.09)

df.percent<-as.data.frame(cbind(Scenario, Percent.combined, Percent.climate, Percent.biodiversity))

df.percent.melt<-melt(df.percent, id="Scenario")

df.percent.melt$Scenario<-factor(df.percent.melt$Scenario, levels=c("Agricultural Productivity", "Climate Adaptation", "Wildlife Habitat","Combined Ecosystem Services"))

df.percent.melt$value<-as.numeric(df.percent.melt$value)

blues<-c("#bdd7e7","#6baed6", "#2171b5")

PercentIndex<-ggplot(df.percent.melt, aes(x = Scenario, fill=variable)) +
  geom_bar(aes(y = value), stat = "identity", position = "dodge") +
  labs(x = "Protection Scenario", y = "Percent High Conservation Value (%)", fill = "Conservation Index") +
  scale_fill_manual(values=blues, labels = c("Combined", "Climate", "Biodiversity"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 35, hjust = 1))+theme(
    axis.text = element_text(size = 12),   # Adjust the font size for tick labels
    axis.title = element_text(size = 14)   # Adjust the font size for axis titles
  )

#--------------------------------#
pixel.combined<-c(0,69,95,70)
pixel.climate<-c(61,164,134,126)
pixel.biodiversity<-c(0,110,133,115)

df.pixel<-as.data.frame(cbind(Scenario, pixel.combined, pixel.climate, pixel.biodiversity))

df.pixel.melt<-melt(df.pixel, id="Scenario")

df.pixel.melt$Scenario<-factor(df.pixel.melt$Scenario, levels=c("Agricultural Productivity", "Climate Adaptation", "Wildlife Habitat", "Combined Ecosystem Services"))

df.pixel.melt$value<-as.numeric(df.pixel.melt$value)

PixelIndex<-ggplot(df.pixel.melt, aes(x = Scenario, fill=variable)) +
  geom_bar(aes(y = value), stat = "identity", position = "dodge") +
  labs(x = "Protection Scenario", y = "Number of High Conservation Value", fill = "Conservation Index") +
 scale_fill_manual(values=blues, labels = c("Combined", "Climate", "Biodiversity"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 35, hjust = 1))+
  theme(
    axis.text = element_text(size = 12),   # Adjust the font size for tick labels
    axis.title = element_text(size = 14)   # Adjust the font size for axis titles
  )

ConservationValue<-PercentIndex+PixelIndex
```

## Bar graphs for ecosystem services

```{r}
 Scenario<-c("Agricultural Productivity", "Combined Ecosystem Services", "Climate", "Wildlife Habitat")

EcosystemServices<-c("Carbon Storage", "Habitat Quality", "Nitrogen Retention","Recreation","Food Production Potential")

#these numbers are taken from caluclations done above
Percent.Ag<-c(7,9,20,6,30) 
Percent.climateAd<-c(30,36,29,31,30) 
Percent.wildlife<-c(27, 30, 27, 24,30) 
Percent.ESc<-c(30,35,30,33,30)


df.percent.ES<-as.data.frame(cbind(EcosystemServices,Percent.Ag, Percent.climateAd, Percent.wildlife, Percent.ESc))

df.percent.ES$EcosystemServices<-factor(df.percent.ES$EcosystemServices, levels=c("Food Production Potential","Carbon Storage", "Habitat Quality", "Recreation", "Nitrogen Retention"))

df.ESp.melt<-melt(df.percent.ES, id="EcosystemServices")
df.ESp.melt$value<-as.numeric(df.ESp.melt$value)

facet_labels <- c(
  "Percent.Ag" = "Agricultural Productivity",
  "Percent.climateAd" = "Climate Adaptation",
  "Percent.wildlife" = "Wildlife Habitat",
  "Percent.ESc" = "Combined Ecosystem Services"
)

viridis_palette <- viridis(5)
palette<-c("#3B9AB2", "#78B7C5","#EBCC2A","#E1AF00","#F21A00")

ESPercent_Facet<-ggplot(df.ESp.melt, aes(x = EcosystemServices, fill=EcosystemServices)) +
  geom_bar(aes(y = value), stat = "identity", position = "dodge") +
  labs(x = "Ecosystem Services", y = "Percent of Ecosystem Service   Protected (%)", fill = "Ecosystem Services") +
scale_fill_manual(values =palette, labels = c("Food Production Potential","Carbon Storage", "Habitat Quality", "Recreation", "Nitrogen Retention"))+
facet_grid(rows = vars(variable), labeller = labeller(variable = facet_labels))+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(
    axis.text = element_text(size = 12),   # Adjust the font size for tick labels
    axis.title = element_text(size = 14)   # Adjust the font size for axis titles
  )

```
